

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins

\name{Fabian Aguilar Gomez} % Your name
\renewcommand{\nameskip}{\smallskip}
\address{(832) 819-7710 - faadnd@utexas.edu - \href{https://github.com/tsusdere}{github/tsusdere}}% Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\normalfont Work Experience}

\begin{rSubsection}{First Community Credit Union}{May 2021 - Present}{Data Analyst}{Houston, TX}
\begin{itemize}[leftmargin=*]
    \item Develop full-stack applications with JavaScript, React, Django, Flask,
    Python, and SQL to replace excel worksheets increasing cooperationg between
    departments by over 75\%. \hspace{4mm}
    \vspace{-1.5mm}
    \item Migrate existent REST APIs to GraphQL, reducing latency across data retrieval, entry, and multiple requests to applications.
     \vspace{-1.5mm}
    \item Automated manual processes and reports by creating stored procedures using SQL and Python scripts saving the company over 20+ hours/week.
     \vspace{-1.5mm}
    \item Deployed workflow applications using C\#, ASP.NET Core, and SQL to
    aid departments cooperate in shared processes decreasing service tickets by 100 daily tickets.
     \vspace{-1.5mm}
    \item Created and set up REST APIs using ASP.NET, Django, and Node.js allowing multiple programs and processes to communicate.
     \vspace{-1.5mm}
    \item Architect and implement data pipelines following ETL using Python
    normalizing future and new data from diverse sources.
\end{itemize}

\end{rSubsection}
\vspace{-3mm}
%------------------------------------------------
\begin{rSubsection}{University of Texas}{September 2019 - June 2021}{Computer Science Tutor}{San Antonio, TX}
\begin{itemize}[leftmargin=*]
    \item Aided over 500+ students with issues involving Linux, Windows, software tools, and programming assignments in Python, Java, C, Unix Shells, and LISP.
    \vspace{-1.5mm}
    \item Influenced student success in rigorous courses such as Data Structures by presenting feedback and alternative methods in over 20 programming assignments and 3 projects.
     \vspace{-1.5mm}
    \item Learned semester's-worth software/language for on average 4 courses on a shortened time frame of 2 months in order to mentor students.
     \vspace{-1.5mm}
\end{itemize}
\end{rSubsection}
\vspace{-5mm}
\begin{rSubsection}{}{}{Mathematics Tutor}{\normalfont September 2018 - September 2019}
\begin{itemize}[leftmargin=*]
    \item Communicated \& assisted over 100+ engineering, business, and science students in their math courses by maintaining a working knowledge of on average 4 college level math courses.
     \vspace{-1.5mm}
    \item Facilitated ongoing math lectures by assisting the professor with administrative duties.
\end{itemize}
\end{rSubsection}
\end{rSection}

\begin{rSection}{\normalfont Side Project}
{\bf Generating Anime} - {\it Python, TensorFlow, OpenCV, NumPy} \hfill {\em January 2021 - May 2021}
\begin{itemize}[leftmargin=*]
\vspace{-1.5mm}
    \item Engineered a deep model that generates 64x64 RGB anime faces from a 100x1 grayscale noise vector.
\end{itemize}


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\normalfont Skills}

\textbf{Languages:} Python, JavaScript, PHP, Golang, SQL, HTML, CSS, Java, C, C++, C\#, LISP

\vspace{-1mm}
\textbf{Database:} MySQL, MongoDB, DynamoDB, PostgreSQL, Microsoft SQL Server

\vspace{-1.5mm}
\textbf{Techonologies:} Git, GraphQL, AWS, Azure, API Development, ASP.NET, Web Services, Open/Closed
Stack, Full-Stack Development, ES6, CI/CD, React, NodeJS, Django, Flask


\end{rSection}

%----------------------------------------------------------------------------------------

%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{\normalfont Education}

{\bf University of Texas at Austin} \hfill {\em August 2021 - May 2023} \\ 
\textit{Master of Science in Computer Science - {\normalfont4.0} GPA}

{\bf University of Texas at San Antonio} \hfill {\em August 2017 - May 2021} \\ 
\textit{Bachelor of Science in Computer Science - {\normalfont3.90} GPA}\\
Data Science Concentration

\end{rSection}


\end{document}
